Jean Pockets and Gender

### 2024-04-23 paper/paper.qmd
update

library(tidyverse)
```

@@

[snap of raw data]

## CSV Dataset and cleaning
Explain how the data was collected and measured

## JSON Dataset and cleaning

# Model
[TBD]

## Model set-up
## Model justification

# Results

>>>>

library(tidyverse)
library(tibble)
library(ggplot2)
library(dplyr)
library(janitor)
library(kableExtra)

## read in raw data 
pocket_area_data = read_csv(
  file = here::here("data/raw_data/pocket_area_data.csv"),
  show_col_types = FALSE
)

## read in cleaned data 
cleaned_area_data = read_csv(
  file = here::here("data/analysis_data/cleaned_area_data.csv"),
  show_col_types = FALSE
)

women_jeans_data = read_csv(
  file = here::here("data/analysis_data/women_jeans_data.csv"),
  show_col_types = FALSE
)

men_jeans_data = read_csv(
  file = here::here("data/analysis_data/men_jeans_data.csv"),
  show_col_types = FALSE
)
```

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-raw_data
#| tbl-cap: "Sample of Raw Pocket Area, Price and Gender Data"

head(pocket_area_data, 5)

```

## JSON Dataset and cleaning
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cleaned_area_data
#| tbl-cap: "Sample of Cleaned Pocket Area, Price and Gender Data"

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd

head (cleaned_area_data, 5) |>
  kable(
    col.names = c("brand","men_women","price","pocket_area"),
  booktabs = TRUE
  )
```

# Model
Given the similarity in lightness observed in foundation shades across both countries, it was of interest to investigate if any differences in saturation existed. This investigation was motivated by the fact that the local population in each country has unique undertones. Before conducting the analysis, several tests were conducted to verify that the model assumptions (See Appendix A), including linearity, normality, and homoscedasticity of residuals, were satisfied, thereby ensuring that the model was well-suited for the data at hand.

The null hypothesis: there is no significant linear relationship between the lightness of foundation shades and the saturation of undertones.

The alternative hypothesis: there is a significant linear relationship between the lightness of foundation shades and the saturation of undertones.

A linear regression analysis can be conducted to test this hypothesis and to determine whether a statistically significant relationship exists between the variables. A low p-value for the regression coefficient for saturation would provide evidence against the null hypothesis, indicating that changes in saturation do result in a meaningful variation in lightness across foundation shades. On the other hand, if the p-value is high, this would suggest that there is not enough evidence to reject the null hypothesis, and there may be no significant linear relationship between the variables. Ultimately, the results of the analysis will inform whether the null hypothesis can be rejected or not. The mathematical equation for the linear regression model can be written as:

$$L = \beta_0 + \beta_1S + \epsilon$$

Where:

- $L$ represents the dependent variable, which is the overall lightness of the foundation shade
- $S$ represents the independent variable, which is the saturation of the foundation shade
- $\beta_0$ represents the intercept of the regression line, which is the predicted value of $L$ when $S$ is equal to zero
- $\beta_1$ represents the slope of the regression line, which is the change in $L$ for a one-unit increase in $S$
- $\epsilon$ represents the random error term, which accounts for variability in $L$ that is not explained by the relationship with $S$

The aim of linear regression is to estimate the values of $\beta_0$ and $\beta_1$ that minimize the sum of squared errors between the predicted and actual values of lightness ($L$) for the given values of saturation ($S$) in the dataset. By minimizing this sum of squared errors, the linear regression model can produce the best-fit line to describe the linear relationship between the two variables, allowing for the estimation of $L$ values based on known $S$ values.

In this project, the lightness variable ($L$) is measured on a scale of 0 to 100, while the saturation variable ($S$) is measured on a scale of 0 to 1. Therefore, the slope coefficient $\beta_1$ in the linear regression model would represent the change in lightness ($L$) for a one-unit increase in saturation ($S$), where a one-unit increase in $S$ corresponds to an increase of 1/100 in the saturation of the foundation shade. The intercept $\beta_0$ in the model would represent the expected value of $L$ when $S$ is equal to zero, which in this case would correspond to the lightness value for a completely desaturated foundation shade.

# Results
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-price_per_pocket_men
#| fig-cap: "Jean Price vs Pocket Size (Men)"

# Create plot for men_jeans_data
men_jeans_plot <- ggplot(men_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "blue") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Area and Price for Men's Jeans",
    x = "Pocket Area (square pixels)",
    y = "Price"
  ) +
  theme_classic()

# Print the plot
men_jeans_plot

# Fit a linear regression model
model <- lm(price ~ pocket_area, data = men_jeans_data)

# View the summary of the model
summary(model)

```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-price_per_pocket_women
#| fig-cap: "Jean Price vs Pocket Size (Women)"

# Create plot for men_jeans_data
women_jeans_plot <- ggplot(women_jeans_data, aes(x = pocket_area, y = price)) +
  geom_point(color = "blue") +
  geom_smooth(method = lm, se = FALSE) +
  labs(
    title = "Pocket Area and Price for Women's Jeans",
    x = "Pocket Area (square pixels)",
    y = "Price"
  ) +
  theme_classic()

# Print the plot
women_jeans_plot

# Fit a linear regression model
model <- lm(price ~ pocket_area, data = women_jeans_data)

# View the summary of the model
summary(model)

```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-price_per_pocket_gender
#| fig-cap: "Jean Price vs. Pocket Area Size per Gender"

## Comparing between average building scores vs.average total income per ward

#Code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd

cleaned_area_data |>
  ggplot(aes(x = pocket_area, y = price, color = men_women)) + 
  geom_point() + 
  geom_smooth(method=lm, se=FALSE) + 
  labs(
    title = "Pocket Area and Price by Gender",
    x = "Pocket Area (square pixels)",
    y = "Price",
    color = "Gender"
  ) +
  scale_color_manual(values = c("blue", "red")) +  # Set custom colors
  theme_classic()
```
